---
title: "Evaluating BERTopic N-gram Configurations on Latvian Exile Press (1940s–2000s): the Coherence Paradox"
author: "Dr. Simon Donig, Dr. Dinara Gagarina, Timur Mitrofanov"
date: "September 17, 2026"
format:
  revealjs:
    theme: white
    slide-number: true
    progress: true
    transition: slide
    controls: true
    width: 1400
    height: 800
    footer: "Evaluating BERTopic N-gram Configurations on Latvian Exile Press (1940s–2000s): the Coherence Paradox"
    embed-resources: false
---
## Topic Word Scores

::: {.panel-tabset}

### Multigram <br><span style="font-size: 0.6em; font-weight: normal; color: gray;">(Words & phrases combined)</span>

<iframe src="multigram_topic_word_scores.html" width="100%" height="620px" style="border:none; border-radius:8px; background:white;" loading="lazy"></iframe>

### Unigram <br><span style="font-size: 0.6em; font-weight: normal; color: gray;">(Single words)</span>

<iframe src="unigram_topic_word_scores.html" width="100%" height="620px" style="border:none; border-radius:8px; background:white;" loading="lazy"></iframe>

### Bigram <br><span style="font-size: 0.6em; font-weight: normal; color: gray;">(Two-word phrases)</span>

<iframe src="bigram_topic_word_scores.html" width="100%" height="620px" style="border:none; border-radius:8px; background:white;" loading="lazy"></iframe>

### Trigram <br><span style="font-size: 0.6em; font-weight: normal; color: gray;">(Three-word phrases)</span>

<iframe src="trigram_topic_word_scores.html" width="100%" height="620px" style="border:none; border-radius:8px; background:white;" loading="lazy"></iframe>

:::

## Detailed Coherence Reports

::: {.panel-tabset}

### Unigram

```{r echo=FALSE, message=FALSE, warning=FALSE}
# load and display unigram data
library(DT)
df_uni <- read.csv("unigram_detailed_coherence_report_lemmatized.csv")
datatable(df_uni, options = list(pageLength = 6, scrollX = TRUE, dom = 'tp'))
```

### Bigram

```{r echo=FALSE, message=FALSE, warning=FALSE}
# load and display bigram data
df_bi <- read.csv("bigram_detailed_coherence_report_lemmatized.csv")
datatable(df_bi, options = list(pageLength = 6, scrollX = TRUE, dom = 'tp'))
```

### Trigram

```{r echo=FALSE, message=FALSE, warning=FALSE}
# load and display trigram data
df_tri <- read.csv("trigram_detailed_coherence_report_lemmatized.csv")
datatable(df_tri, options = list(pageLength = 6, scrollX = TRUE, dom = 'tp'))
```

### Multigram

```{r echo=FALSE, message=FALSE, warning=FALSE}
# load and display multigram data
df_multi <- read.csv("multigram_detailed_coherence_report_lemmatized.csv")
datatable(df_multi, options = list(pageLength = 6, scrollX = TRUE, dom = 'tp'))
```

:::

## Hierarchical Clustering (multigram)

```{=html}
<iframe src="nested_bertopic.html" width="100%" height="680px"
  style="border:none; border-radius:8px; background:white;" loading="lazy"></iframe>
```

## Intertopic Distance Map 

::: {.panel-tabset}

### Multigram <br><span style="font-size: 0.6em; font-weight: normal; color: gray;">(Words & phrases combined)</span>

<iframe src="multigram_intertopic_distance_map.html" width="100%" height="680px" style="border:none; border-radius:8px; background:white;" loading="lazy"></iframe>

### Unigram <br><span style="font-size: 0.6em; font-weight: normal; color: gray;">(Single words)</span>

<iframe src="unigram_intertopic_distance_map.html" width="100%" height="680px" style="border:none; border-radius:8px; background:white;" loading="lazy"></iframe>

### Bigram <br><span style="font-size: 0.6em; font-weight: normal; color: gray;">(Two-word phrases)</span>

<iframe src="bigram_intertopic_distance_map.html" width="100%" height="680px" style="border:none; border-radius:8px; background:white;" loading="lazy"></iframe>

### Trigram <br><span style="font-size: 0.6em; font-weight: normal; color: gray;">(Three-word phrases)</span>

<iframe src="trigram_intertopic_distance_map.html" width="100%" height="680px" style="border:none; border-radius:8px; background:white;" loading="lazy"></iframe>

:::

## Topics Over Time

::: {.panel-tabset}

### Multigram <br><span style="font-size: 0.6em; font-weight: normal; color: gray;">(Words & phrases combined)</span>

<iframe src="multigram_topics_over_time.html" width="100%" height="650px" style="border:none; border-radius:8px; background:white;" loading="lazy"></iframe>

### Unigram <br><span style="font-size: 0.6em; font-weight: normal; color: gray;">(Single words)</span>

<iframe src="unigram_topics_over_time.html" width="100%" height="650px" style="border:none; border-radius:8px; background:white;" loading="lazy"></iframe>

### Bigram <br><span style="font-size: 0.6em; font-weight: normal; color: gray;">(Two-word phrases)</span>

<iframe src="bigram_topics_over_time.html" width="100%" height="650px" style="border:none; border-radius:8px; background:white;" loading="lazy"></iframe>

### Trigram <br><span style="font-size: 0.6em; font-weight: normal; color: gray;">(Three-word phrases)</span>

<iframe src="trigram_topics_over_time.html" width="100%" height="650px" style="border:none; border-radius:8px; background:white;" loading="lazy"></iframe>

:::
<!--
## Geographical and Geopolitical entities

```{=html}
<iframe src="Map_timeline.html" width="100%" height="680px"
  style="border:none; border-radius:8px; background:white;" loading="lazy"></iframe>
```

## Most Mentioned Country by Month and Year
```{=html}
<iframe src="country_mentions_interactive.html" width="100%" height="680px"
  style="border:none; border-radius:8px; background:white;" loading="lazy"></iframe>
```

## Entities identified by GLiNER 
```{=html}
<iframe src="extracted_entities.html" width="100%" height="680px"
  style="border:none; border-radius:8px; background:white;" loading="lazy"></iframe>
```
-->